Learning \strips\ Action Models with Classical Planning

### 2018-04-18 doc/aij18/background.tex
new paper organization

\section{Related work}
\label{sec:Section2}

@@

We will refer to a state sequence as $\Sigma = \langle s_0, s_1, \ldots, s_n \rangle$ and an action sequence as $\Omega = \langle a_1, a_2, \ldots, a_n \rangle$. In a full observable (FO) state sequence $\Sigma$, every state $s_i \in \Sigma$ is a complete state and the minimal action sequence to transit from state $s_i$ to state $s_{i+1}$  is given by $\Omega = \langle a_{i+1} \rangle$. On the other hand, $\Omega$ is a FO action sequence if there are no missing actions in $\Omega$.

A plan trace is a combination of a state and an action sequence $\tau = \langle s_0, a_1, a_1, a_2, s_2, \ldots, a_n, s_n \rangle$. Additionally, $\tau$ is a plan trace with partial observable (PO) states if there is at least one missing literal in any state $s_i$. And $\tau$ is a plan trace with PO actions of there is at least one missing action from the action sequence.

@@

>>>>

\section{Background}
\label{sec:background}

This section serves two purposes. In subsection \ref{basic_planning} we introduce the basic planning concepts as well as the classical planning model that we will use throughout the rest of the paper. Section \ref{related_work} summarizes existing approaches to learning action models in classical planning and highlights the novelty of our contribution via the related work.

%This section defines the planning model used on this work, {\em classical planning with conditional effects}, and the target of the learning/evaluation/recognition tasks addressed in the paper, a \strips\ action model.

\subsection{Basic planning concepts}
\label{basic_planning}

We use $F$ to denote the set of {\em fluents} (propositional variables) describing a state. A {\em literal} $l$ is a valuation of a fluent $f\in F$, i.e. either~$l=f$ or $l=\neg f$. A set of literals $L$ represents a partial assignment of values to fluents (without loss of generality, we will assume that $L$ does not assign conflicting values to any fluent). We use $\mathcal{L}(F)$ to denote the set of all literal sets on $F$, i.e.~all partial assignments of values to fluents.

A {\em state} $s$ is a full assignment of values to fluents, i.e. $|s|=|F|$, so the size of the state space is $2^{|F|}$. Explicitly including negative literals $\neg f$ in states simplifies subsequent definitions but often, we will abuse notation by defining a state $s$ only in terms of the fluents that are true in $s$, as is common in \strips\ planning.

A {\em classical planning frame} is a tuple $\Phi=\tup{F,A}$, where $F$ is a set of fluents and $A$ is a set of actions. An action $a\in A$ is defined with:

%{\em preconditions}, $\pre(a)\subseteq\mathcal{L}(F)$, {\em negative effects} $\eff^-(a)\subseteq\mathcal{L}(F)$ and {\em positive effects}, $\eff^+(a)\subseteq\mathcal{L}(F)$.

\begin{itemize}
\item $\pre(a)\in\mathcal{L}(F)$, the {\em preconditions} of $a$, is the set of literals that must hold for the action $a\in A$ to be applicable.
\item $\eff^+(a)\in\mathcal{L}(F)$, the {\em positive effects} of $a$, is the set of literals that true after the application of the action $a\in A$.
\item $\eff^-(a)\in\mathcal{L}(F)$, the {\em negative effects} of $a$, is the set of literals that are false after the application of the action.
\end{itemize}

We say that an action $a\in A$ is {\em applicable} in a state $s$ iff $\pre(a)\subseteq s$. The result of applying $a$ in $s$ is the {\em successor state} denoted by $\theta(s,a)=\{s\setminus\eff^-(a))\cup\eff^+(a)\}$.

A {\em classical planning problem} is a tuple $P=\tup{F,A,I,G}$, where $I$ is an initial state and $G\in\mathcal{L}(F)$ is a goal condition. A {\em plan} for $P$ is an action sequence $\pi=\tup{a_1, \ldots, a_n}$ that induces the {\em state trajectory} $\tup{s_0, s_1, \ldots, s_n}$ such that $s_0=I$ and, for each {\small $1\leq i\leq n$}, $a_i$ is applicable in $s_{i-1}$ and generates the successor state $s_i=\theta(s_{i-1},a_i)$. The {\em plan length} is denoted with $|\pi|=n$ . A plan $\pi$ {\em solves} $P$ iff $G\subseteq s_n$, i.e.~if the goal condition is satisfied at the last state reached after following the application of the plan $\pi$ in the initial state $I$.

In this work, we will use the term \emph{observation} to refer to the input knowledge of a learning task. Hence, $\tup{s_0, s_1, \ldots, s_n}$ is a full observable (FO) state trajectory if every state $s_i$ is a full assignment of values to fluents and the minimal action sequence to transit from state $s_i$ to state $s_{i+1}$ is composed of a single action; that is, $\theta(s_i,a)=s_{i+1}$. Otherwise, $\tup{s_0, s_1, \ldots, s_n}$ is a partial observable (PO) state trajectory, meaning that at least one $s_i$ is a partial assignment of values to fluents in which one or more literals are missing. Likewise, $\tup{a_1, \ldots, a_n}$ is a FO action sequence if it contains all the necessary actions to achieve a goal from an initial state, and a PO action sequence if at least one necessary action is missing in the sequence.

A \emph{plan trace} is a combination of a state and an action sequence $\tau = \langle s_0, a_1, a_1, a_2, s_2, \ldots, a_n, s_n \rangle$. Additionally, $\tau$ is a plan trace with PO states if $\tup{s_0, s_1, \ldots, s_n}$ is a PO state sequence and a plan trace with PO actions if $\tup{a_1, \ldots, a_n}$ is a PO action sequence.

\subsection{Related work}
\label{related_work}

@@

@@

The Crowdsourced Action-Model Acquisition (\CAMA) for planning explores knowledge from both crowdsourcing (human annotators) and plan traces to learn action models for planning. \CAMA relies on the assumption that obtaining enough training samples is often difficult and costly because there is usually a limited number of plan traces available. In order to overcome this limitation, \CAMA builds on a set of soft constraints based on labels \texttt{true} or \texttt{false} given by the crowd and a set of soft constraints based on the input plan traces, solves then using a MAX-SAT solver and converts the solution to action models.

\CAMA uses plan traces with PO states. To capture the knowledge from the crowd, \CAMA enumerates all possible preconditions and effects for each action, considering all predicates whose parameters are included by the parameters of the action. Hence, if the parameters of a predicate $p$ are included by the parameters of $a$, \CAMA queries the crowd for three questions of the form "Is the fact $p$ a precondition/positive effect/negative effect of action $a$?", and human annotators reply "yes", "no" or "cannot tell". The goal is to find an optimal estimator of the \texttt{true} labels given the observation, minimizing the average bit-wise error rate.

================================================
